## About `Shiny SimDisplay`

Thank you for checking out this interactive applet! This application is part of the [SimDisplay](https://github.com/mattsigal/SimDisplay) package. It was written as a component of Matthew Sigal’s dissertation (*Everything on the table: Tabular, graphic, and interactive approaches for interpreting and presenting Monte Carlo simulation data*), which was completed at York University under the supervision of Dr. Michael Friendly, Dr. Robert Cribbie, and Dr. David Flora.

The goal of this application is to allow for the exploration of Monte Carlo simulation study results produced by [SimDesign](https://github.com/philchalmers/SimDesign/). Multiple views of simulation results are afforded.

## Launching the Application

To install this application, simply paste the following code in the `R` console:

```{r, eval=FALSE}
devtools::install_github("mattsigal/SimDisplay")
library(“SimDisplay”)
```

Once the `SimDisplay` package has been installed and loaded, the `shiny` application can be initialized via:

```{r, eval=FALSE}
shinyMCSS()  # To run with the default dataset
```

You can also pass any dataset object (of class `SimDesign`) to the function to utilize your own data within the application:

```{r, eval=FALSE}
library(“SimDisplay”)
data(“Brown1974”)
shinyMCSS(Brown1974)
```

## Instructions

The application is organized from left to right. The left-most tab pertains to the **Data Explorer**. This is a `datatable` view of the results. Filters applied in this window will subset the data for the functions in the other tabs. The **Models** tab can be used to generate and inspect ANOVA and MANOVA models for the MCSS results (note: Generating a MANOVA model is required to produce some of the visualizations). The final tab pertains to various **Graphical Methods** for inspecting MCSS results, namely via semi-graphic tables, tableplots, boxplots, and HE plots.

## Want to help?

Contributions to the application are encouraged. To do so, please fork the `SimDisplay` repo and create a pull request. Additionally, you can report bugs and feature requests [here](https://github.com/mattsigal/SimDisplay/issues).

## Author

Matthew Sigal | matthewsigal@gmail.com

## Credit

This application was developed with [shiny](http://shiny.rstudio.com/) in 
[Rstudio](https://www.rstudio.com/).

